---
title: "R Notebook"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

```{r}
library(dplyr);
library(boot);
library(broom);
library(knitr);
library(ggplot2);
data <- read.csv("analysis/data.csv", comment.char ="#");
data[data=="true"] <- 1;
data[data=="false"] <- 0;
data <- transform(data, wasSuccessful = as.numeric(wasSuccessful))
boot_mean <- function(original_vector, resample_vector) {
    mean(original_vector[resample_vector])
}
```

```{r}
questions<-list(
"I had to re-read instructions to understand what I needed to do",
"It was always clear to me what I was supposed to do.",
"Overall, the system gave me good instructions.",
 "The system gave me useful feedback about my progress.",
 "The system was really verbose and explained things that were already clear to me.",
 "The system's  instructions came too early.",
 "The system's  instructions came too late."
)
```

# Evaluation of *all* games (i.e. building might not be finished)

note that timings are probably highly correlated with successfulness here!
```{r}
data
```



```{r, results='asis'}

feats <- list("timeToSuccess", "numMistakes", "Question0", "Question1", "Question2", "Question3", "Question4",  "Question5", "Question6")

architects <- list("BLOCK", "MEDIUM", "HIGHLEVEL")

bridgetableall<-data.frame(matrix(nrow=length(feats), ncol=3))
colnames(bridgetableall) <- architects
row.names(bridgetableall) <- feats
housetableall<-data.frame(matrix(nrow=length(feats), ncol=3))
colnames(housetableall) <- architects
row.names(housetableall) <- feats


for (scen in list("house", "bridge")) {
  cat('\n\n##' , scen , '\n\n')
  for (q in list("wasSuccessful", "numMistakes", "Question0", "Question1", "Question2", "Question3", "Question4",  "Question5", "Question6")) {
    cat('\n\n###', q, '\n')
    for (arch in list("BLOCK", "MEDIUM", "HIGHLEVEL")) {
      cat('\n####', arch, '\n\n')
      nam <- paste("succ",scen,arch, sep="")
      assign(nam, data %>% filter(scenario == scen) %>% filter(architect == paste("SimpleArchitect-",arch, sep="")), envir = .GlobalEnv)

      dset <- get(nam)[,c(q)]
      # hist(dset)
      cat('\n\n')
      mean_results <- boot(dset, boot_mean, R = 200);
      print(boot.ci(mean_results, type="bca"))
      cat('\n\n')
      print(kable(tidy(summary(dset)), align="llllll" ))
      
      if (scen == "house") {
        housetableall[q, arch] <- mean(dset)[1]
      } else {
        bridgetableall[q, arch] <- mean(dset)[1]
      }
      
    }
  }
}
```



 - Question0: I had to re-read instructions to understand what I needed to do
 - Question1: It was always clear to me what I was supposed to do.
 - Question2: Overall, the system gave me good instructions.
 - Question3: The system gave me useful feedback about my progress.
 - Question4: The system was really verbose and explained things that were already clear to me.
 - Question5: The system's  instructions came too early. 
 - Question6: The system's  instructions came too late. 




# Evaluation of successful games (i.e. building was finished)

```{r, results='asis'}

# "HLO0", "HLO1", "HLO2",

feats <- list("timeToSuccess", "numMistakes", "Question0", "Question1", "Question2", "Question3", "Question4",  "Question5", "Question6")

architects <- list("BLOCK", "MEDIUM", "HIGHLEVEL")

bridgetable<-data.frame(matrix(nrow=length(feats), ncol=3))
colnames(bridgetable) <- architects
row.names(bridgetable) <- feats
housetable<-data.frame(matrix(nrow=length(feats), ncol=3))
colnames(housetable) <- architects
row.names(housetable) <- feats

housetable["timeToSuccess", "BLOCK"] <- 1

succGames <- data %>% filter(wasSuccessful == 1);
for (scen in list("house", "bridge")) {
  cat('\n\n##' , scen , '\n\n')
  for (q in feats) {
    cat('\n\n###', q, '\n')
    for (arch in architects) {
      cat('\n####', arch, '\n\n')
      nam <- paste("succ",scen,arch, sep="")
      assign(nam, succGames %>% filter(scenario == scen) %>% filter(architect == paste("SimpleArchitect-",arch, sep="")), envir = .GlobalEnv)

      dset <- get(nam)[,c(q)]
      # hist(dset)
      cat('\n\n')
      mean_results <- boot(dset, boot_mean, R = 200);
      print(boot.ci(mean_results, type="bca"))
      cat('\n\n')
      print(kable(tidy(summary(dset)), align="llllll" ))
      if (scen == "house") {
        housetable[q, arch] <- mean(dset)[1]
      } else {
        bridgetable[q, arch] <- mean(dset)[1]
      }
    }
  }
}

```

 - Question0: I had to re-read instructions to understand what I needed to do
 - Question1: It was always clear to me what I was supposed to do.
 - Question2: Overall, the system gave me good instructions.
 - Question3: The system gave me useful feedback about my progress.
 - Question4: The system was really verbose and explained things that were already clear to me.
 - Question5: The system's  instructions came too early. 
 - Question6: The system's  instructions came too late. 

# compact tables

## all games

### means for bridge (all)

```{r}
kable(bridgetableall, digits=2)
```


### means for house (all)

```{r}
kable(housetableall, digits=2)
```


## successful games

### means for bridge (successful only)

```{r}
kable(bridgetable, digits=2)
```


### means for house (successful only)

```{r}
kable(housetable, digits=2)
```
